---
title: "Assignment 01: Set up"
author: Your name
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::pdf_document2:
    toc: false
    number_sections: true
    latex_engine: pdflatex
    keep_tex: false
    fig_caption: true
fontfamily: mathpazo
fontsize: 11pt
---

# Overview

## Purpose {-}

The purpose of this assignment is twofold.

1. To check if your computation environment is up and running; and
2. To become familiar with GitHub workflow

## Goal {-}

- Clone the assignment repository
- Make a working branch
- Replicate the present PDF file with your name on the author line
- Commit the change and send a Pull Request
 
# Prerequisite

## GitHub Account {-}

Make a github account if you don't have one.

- [GitHub](https://github.com/)

## Softwares {-}

Please install the following softwares (they are free)

- R 
- RStudio
- LaTeX system ([texlive for Windows/Linux](https://www.tug.org/texlive/), 
  [MacTeX for macOS](https://tug.org/mactex/))
- [GitHub Desktop](https://desktop.github.com/)

When you finish installation, follow the instructions.

# Instructions

## Step 1. Clone the assignment repository {-}

Click the invitation link. Your assignment repository is automatically created. 
Click "Clone or download" and then click "Open in Desktop". Then GitHub Desktop
opens.

## Step 2. Make a new brach with a descriptive name {-}

Do not start to work on the problem yet! Make a new branch with a descriptive name. 
Let's say, "workbench". 

## Step 3. Open the assignment directory by RStudio {-}

Then open the folder in which the repository resides, by 

- [Windows] Clicking the gear button and then "Open in Explorer"
- [Mac] Right-Clicking (Two-finger click) on the repository name in the left area, 
  and then clicking "Open in Finder"

Double click "*.Rproj" file. RStudio should open. 

## Step 4. Open this assignment file {-}

Look at the "Files" pane on RStudio. Open "01-setup" and click "problem.Rmd". 
Now you see the source file of this instruction manual. 


## Step 5. Knit {-}

Click "knit" button above the editor pane. If this is the first time you 
try to knit Rmd to PDF you are prompted to install and/or update dependencies. 
Success?

Now, do you see the rendered PDF file? Congratulations, you are good to go!

If you don't see the PDF, hang in there. Since this is typical, don't 
be ashamed of having caused an error. As you learn how to code, you'll 
read even more error messages (not less!!).

What you need to do is read the error message carefully. Try to figure out 
what is missing.After a careful reading of error message, you sometimes can 
fix it yourself. But not always. If you still don't know what to do, copy 
the error message and ask google about that. If you still can't fix,
ask the TA or lecturer.

Your problem was probably caused by a missing packages? As a matter of fact, 
this Rmd depends on not-preinstalled package called "tidyverse". 
Please install this.

```{r, eval=FALSE}
install.packages("bookdown")
install.packages("tidyverse")
```

`install.packages("package_name")` is a typical way of package installation on R.

## Step 6. Make modification {-}

You may want to modify the source because the output PDF file has strange author 
name on it: "Your name". Find the way to change the author name. Put your name there.

And save the file and knit again.



# Example text

## Data analysis

```{r}
library(tidyverse)
(iris_tbl <- as_data_frame(iris))
```

The following code produce Figure \@ref(fig:iris).^[See http://stackoverflow.com/questions/38861041/knitr-rmarkdown-latex-how-to-cross-reference-figures-and-tables/38884378#38884378]

```{r iris, fig.cap="Iris Data", fig.align='center', fig.width=4, fig.height=3}
ggplot(iris_tbl) + 
  geom_point(aes(x = Sepal.Length, y = Petal.Length, color = Species)) 
```

## Matheamtical equation

Using LaTeX syntax, you can produce mathematical equations: 

\begin{equation}
f(x) = f(0) + \int_0^x f'(y) dy.  (\#eq:ftc)
\end{equation}


Cross reference works like Equation \@ref(eq:ftc) but the syntactic rule is different from LaTeX. 
See [https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html#equations](https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html#equations) for more detail.


